\documentclass[10pt]{article} 

\input{structure.tex} 

\begin{document}

\title{Spiros Gerokostas -- Résumé} 

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Kalamon 10,\\ % Address line 1
\> Ampelokipoi, Athens, 11526 \\ % Address line 2
{\bf Date of Birth} \> 22 February 1982 \\ % Date of birth 
{\bf Home Phone} \> 211 0101746 \\ % Home phone
{\bf Mobile Phone} \>+30 6940772386 \\ % Mobile phone
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Personal Website:} \>\href{https://www.spirosgerokostas.com}{https://www.spirosgerokostas.com} \\ % Website
{\bf Email:} \> \href{mailto:spiros.gerokostas@gmail.com}{spiros.gerokostas@gmail.com} \\ % Email address
{\bf Skype:} \> spiros.gerokostas \\ % Skype
{\bf GitHub:} \>\href{http://github.com/sger}{github.com/sger} \\ % GitHub
{\bf Twitter:} \>\href{http://twitter.com/sger}{twitter.com/sger} \\ % Twitter
{\bf Updated:} \> 08/04/2020 \\ % Updates
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Software Engineer}

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Feb 2019 -}{Current}
{Beat}
{http://www.thebeat.co}
{Lead iOS Engineer}
{Development on Driver and Passenger application.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Objective C/Swift}

\job
{March 2017 -}{Feb 2019}
{Unify/Atos}
{http://unify.com}
{Software Engineer}
{Lead development on OpenScape iOS VoIP application.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Objective C/Swift, C/C++, Java, Jenkins, Travis CI.}

\job
{July 2015 -}{Feb 2017}
{Freelance}
{http://github.com/sger}
{Software Engineer}
{Working with clients Upstream systems, Convoy interactive agency, Verisys, Trebbble, Wind.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Objective C/Swift, Laravel, Bootstrap, JQuery, Vue.js, Docker, Rabbitmq, Memcached, Jenkins, Travis CI.}

%------------------------------------------------

\job
{June 2015 -}{July 2015}
{Tapely}
{https://tapely.com}
{Senior iOS Developer}
{Lead development on iOS apps Tapely and Night.Tapely is a music platform about creating music mixtapes using YouTube and SoundCloud APIs.Night is a social music app available only during the NIGHT.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Autolayout, UIKit, Core Audio, SoundCloud API, Facebook Graph API, Twitter API, Google API.}

%------------------------------------------------


\job
{May 2014 -}{Jun 2015}
{Pockee}
{http://www.pockee.com}
{Software Engineer}
{Employee number one.Lead development on iOS and Android version.Pockee is a mobile coupon application for super-markets.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Autolayout, Core Data, Location services API, QR Reader, MySQL, PHP (Laravel), Facebook Graph API, Twitter API, Google API.}

%------------------------------------------------

\job
{2010 -}{2014}
{TribalDDB Athens}
{http://www.tribalddb.gr}
{Interactive Developer}
{Clients Toyota Hellas, VW London, Dewars
\\
\rule{0mm}{5mm}\textbf{Technologies:} Objective C, PHP, Drupal, Wordpress, MySQL, JQuery, HTML 5, Adobe Flash.}

%------------------------------------------------

\job
{2008 -}{2009}
{OgilvyOne Athens}
{http://www.ogilvyone.gr}
{Web Developer}
{Clients Nestle, OTE, Cosmote
\\
\rule{0mm}{5mm}\textbf{Technologies:} PHP, Drupal, MySQL, JQuery, Adobe Flash.}

%------------------------------------------------

\job
{2006 -}{2008}
{Onyro EVS}
{http://www.onyro.com}
{Web Developer}
{Clients Saatchi and Saatchi New York, Olympiacos
\\
\rule{0mm}{5mm}\textbf{Technologies:} PHP, MySQL, Adobe Flash.}

%----------------------------------------------------------------------------------------
%	EXPERIENCE - PRODUCTS
%---------------------------------------------------------------------------------------

\section{Experience/Products}

\job
{2016}{}
{RxMKMapView}
{https://github.com/RxSwiftCommunity/RxMKMapView}
{\href{https://github.com/RxSwiftCommunity/RxMKMapView/}{https://github.com/RxSwiftCommunity/RxMKMapView}}
{RxMKMapView is a RxSwift wrapper for MKMapView `delegate`.}

\job
{2016}{}
{Locito}
{http://loci.to}
{\href{http://www.mokaal.com/index.html}{Created for Mokaal}}
{Locito is a mobile app that allows users to find and interact with fun and exciting places around them.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Autolayout, Core Location, Google Maps API, Google Directions API, MongoDB, Node.js, Augmented Reality, QR, JSON, Rest API}

\job
{2015}{}
{Laisne - Roussel Architects}
{http://laisneroussel.com/}
{\href{http://www.convoy.me}{Created for Convoy interactive agency located in Paris}}
{Developed a content management system with Laravel framework and React.js.
\\
\rule{0mm}{5mm}\textbf{Technologies:} PHP, Laravel, Memcached, React.js, JSON, Rest API, MySQL}

\job
{2015}{}
{Bitcoin Currency}
{http://www.spirosgerokostas.com/bitcoin-currency/}
{\href{https://itunes.apple.com/us/app/bitcoin-currency/id946708232?ls=1&mt=8}{Bitcoin Currency App Store}}
{A simple bitcoin converter for iOS Devices
\\
\rule{0mm}{5mm}\textbf{Technologies:} UIKit, Autolayout, JSON, Rest API}

\job
{2015}{}
{Tinylog}
{http://binarylevel.github.io/tinylog/}
{\href{https://github.com/binarylevel/Tinylog-iOS}{Tinylog}}
{Tinylog is a minimal TODO App for iOS (iPhone/iPad) also Tinylog is the first product of my self-funded company Binary Level.
\\
\rule{0mm}{5mm}\textbf{Technologies:} UIKit, Autolayout, Core Data, iCloud services, Local notifications, Reminders}

\job
{2014}{}
{Pastepasswd}
{https://github.com/sger/Pastepasswd}
{\href{http://www.spirosgerokostas.com/paste-passwd/}{Pastepasswd}}
{A simple password generator for iOS Devices also Pastepasswd is an open source project.
\\
\rule{0mm}{5mm}\textbf{Technologies:} UIKit}

\job
{2012}{}
{Clipr}
{http://www.clipr.io}
{\href{https://itunes.apple.com/us/app/clipr/id582636684?ls=1&mt=8&2}{Clipr for iOS}}
{Lead development on iOS app.Clipr brings forward articles you want to recollect and delivers them to you, at a preferred place and time.
\\
\rule{0mm}{5mm}\textbf{Technologies:} PHP (Yii framework), Core Data, Core Location Services, Facebook Graph API, Twitter API, Google API}

\job
{2011}{}
{Caprice Countdown}
{https://itunes.apple.com/gr/app/caprice-countdown/id705833726?mt=8}
{\href{https://play.google.com/store/apps/details?id=air.CapriceIceAndroid}{Caprice Countdown Android version}}
{Lead development on iOS and Android game Caprice Countdown for papadopoulou.gr.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Facebook Graph API, Twitter API, Google API}

\job
{2011}{}
{Help Me Sleep}
{https://itunes.apple.com/gr/app/helpmesleep-ikea/id643225424?mt=8}
{\href{https://play.google.com/store/apps/details?id=air.HelpMeSleep}{Help Me Sleep Android version}}
{Lead development on iOS and Android app Help Me Sleep for IKEA Greece.
\\
\rule{0mm}{5mm}\textbf{Technologies:} Facebook Graph API, Twitter API, Google API}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\education
{2014 - 2018}{}
{Hellenic Open University - Computer Science}
{http://www.eap.gr/index.php?lang=el}

%------------------------------------------------

\education
{2000 - 2002}{}
{IEK Multimedia}
{}

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Programming Languages}
{
\textit{Objective C/Swift}\\
\textit{C/C++}\\
\textit{Go}\\
\textit{Erlang/Elixir}\\
\textit{PHP}\\
}

%------------------------------------------------

\skillgroup{Web Development}
{
\textit{Laravel,Symfony}\\
\textit{Phoenix}\\
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{MySQL,PostgreSQL} - database architecture and administration\\
\textit{MongoDB} - database architecture and administration\\
\textit{Redis, Memcached} - database architecture and administration\\
\textit{Git} - source version control\\
\textit{Amazon Web Services}\\
\textit{Docker}\\
\textit{RabbitMQ}\\
}


\end{document}